Dependent Object Types

### 2012-08-07 article.tex
fix
fix tsel-wf1 rule
typo

There are four alphabets: Variable names $x$, $y$, $z$ are freely
alpha-renamable. They occur as parameters of lambda abstractions, as
binders for objects created by \verb@new@-expressions, and as self
references in refinements. Value labels $l$ denote fields in objects,
which are bound to values at run-time. Similarly, method labels $m$
denote methods in objects. Type labels $L$ denote type members of
objects. Type labels are further separated into labels for abstract
types $L_a$ and labels for classes $L_c$. It is assumed that in each
program every class label $L_c$ is declared at most once.

@@

      \infrule[\textsc{tsel-wf$_1$}]
      {\Gamma \ts p \ni \Ldecl L S U \spcomma S \wf \spcomma U \wf}
      {\Gamma \ts p.L \wf \spcomma p.U \wf}

@@

\subsubsection{$\mathcal{G}$}
$\relg k s \Gamma$ defines a singleton set of a completed environment
that agrees with a store $s$ by simply copying the constructor type
from the store for each missig variable.
\begin{align*}
&\relg k s \Gamma = \{ \Gamma, \seq{x_i : T_{c_i}}^{m \leq i < n} \ |\\
&\gap \Gamma = \seq{x : T}^m \andl s = \seq{x \mapsto c}^n \andl\\
&\}
\end{align*}

>>>>

There are four alphabets: Variable names $x$, $y$, $z$ are freely
alpha-renamable. They occur as parameters of methods, as
binders for objects created by \verb@new@-expressions, and as self
references in refinements. Value labels $l$ denote fields in objects,
which are bound to values at run-time. Similarly, method labels $m$
denote methods in objects. Type labels $L$ denote type members of
objects. Type labels are further separated into labels for abstract
types $L_a$ and labels for classes $L_c$. It is assumed that in each
program every class label $L_c$ is declared at most once.

@@

      \infrule[\textsc{tsel-wf$_1$}]
      {\Gamma \ts p \ni \Ldecl L S U \spcomma S \wf \spcomma U \wf}
      {\Gamma \ts p.L \wf}

@@

\subsubsection{$\mathcal{G}$}
$\relg k s \Gamma$ defines a singleton set of a completed environment
that agrees with a store $s$ by simply copying the constructor type
from the store for each missing variable.
\begin{align*}
&\relg k s \Gamma = \{ \Gamma, \seq{x_i : T_{c_i}}^{m \leq i < n} \ |\\
&\gap \Gamma = \seq{x : T}^m \andl s = \seq{x \mapsto c}^n \andl\\
&\}
\end{align*}
